Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-11-24 Response/Response 3/reviewer_response.tex

	\title{Reviewers Comments \& Authors Replies}

	\date{}
	\maketitle

	\begin{tabular}{p{1.25in}p{4.25in}}
		\textbf{Manuscript No.} & Paper T-SP-18051-2014, submitted to \emph{``IEEE Transactions on Signal Processing"} \\ \\
		\textbf{Title} & ``Traffic Aware Resource Allocation Schemes for Multi-Cell MIMO-OFDM Systems" \\ \\
		\textbf{Authors} & Ganesh Venkatraman, Antti T\"{o}lli, Markku Juntti, and Le-Nam Tran
	\end{tabular}

	\vspace{0.35in}
	The authors are grateful to the associate editor for giving us an additional opportunity to revise and correct our convergence analysis. In this regard, we would like to give a special thank to Review 3 who pointed out the issues with our convergence analysis of the proposed solutions. In this revision, we have mainly focused on providing a more mathematically rigorous  proof of the convergence analysis of the proposed iterative algorithms.
	%\input{additions}
	Towards this end the following changes have been made to the revised manuscript.
	\begin{enumerate}
		\item We have restated the convergence results of the centralized algorithms in this revision, claiming that any accumulated point (i.e., a limit point) is a stationary point. The proof is essentially based on the convergence of a subsequence of iterates. We have rewritten Appendix A-D according to these changes. In particular, to discuss the convergence of the sequence of iterates generated by the centralized method, we use a unified superscript index \eqn{t} to refer to the step index of both \ac{AO} and \ac{SCA} procedures (\textit{i.e.}, index \eqn{t} denotes \ac{SCA} and \ac{AO} update step (\eqn{k,i})). Using this index \eqn{t}, we denote iterate \eqn{\ma^t} as a stacked vector of the minimizer obtained by solving convex subproblem \eqref{con-m} at each step \eqn{t} as \eqn{\mat{t} = \mbf{z}^{(i)}_k} for some \ac{SCA} and \ac{AO} iteration. Using this notation, we have revised our convergence discussions in Appendices A-C and A-D.		
		\item We have updated the convergence of distributed algorithms in a similar way.
	\end{enumerate}

	We have  also revised some parts of text to support the changes mentioned above and to further improve the readability. Specifically, the following parts of the revision have been rewritten.
	\begin{itemize}
		\item Page 6, paragraph after (28): We have elaborated the discussions on showing that the feasible set is bounded.
		\item Page 8, last paragraph in Section IV-B: We discussed the conditions under which the overall algorithm converges upon using the distributed schemes in each \ac{SCA} step.
		\item Last sentence after (51) on page 14: We emphasized the convergence of objective sequence only in each \ac{AO} step. 
		\item Last sentence after (60) on page 15: We have rewritten the convergence claim on the sequence of iterates generated by the Algorithm 2 similar to that of centralized method.
	\end{itemize}

	\vspace{1eM}
	In what follows, the comments are listed, each followed immediately by the corresponding reply from the authors. The reviewers questions in the revised manuscript are highlighted in blue color and the authors responses are presented in black. Unless otherwise stated, all the numbered items (figures, equations, references, citations, etc) in this response letter refer to the revised manuscript. All revisions in the manuscript are highlighted in blue color.
	\newpage
	\section*{Response to first reviewer comments}
	\input{response-1}

### 2015-11-24 Report/convergence_centralized.tex
updated and finalized

The following conditions are required to show the convergence of Algorithm \ref{algo-1}, which is used to solve problems \eqref{eqn-6} and \eqref{eqn-mse-1} in an iterative manner.
\begin{itemize}
\item[(a)] Uniqueness of the minimizer in each step
\item[(b)] Objective function should be bounded below
\item[(c)] Feasible set should be compact
\item[(d)] Sequence of objective values should be strictly decreasing
\end{itemize}
Upon satisfying (a)-(d), we can show the convergence of the objective sequence generated by the Algorithm \ref{algo-1}, using \cite[Th. 3.14]{rudin1964principles}. However, it is not  sufficient enough to ensure the convergence of the corresponding sequence of iterates. Therefore, by following the discussions in \cite{marks1978technical,lanckriet2009convergence,scutari_1}, we can only claim that \reviewF{every limit point of the sequence of iterates generated by the iterative method is a stationary point of original nonconvex formulations in \eqref{eqn-6} and \eqref{eqn-mse-1}}.

@@

To ensure the uniqueness of the transmit and the receive beamformers, the objective function of the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} are regularized by a strongly convex function in each \ac{SCA} iteration \eqn{k} and \ac{AO} update step \eqn{i} as 
\begin{IEEEeqnarray}{rCl} \neqsub
\hat{f}(\mbf{z}) &=& \| \tilde{\mbf{v}} \|_q \eqsub \label{orig_obj} \\ 
f(\mbf{z}) &=& \hat{f}(\mbf{z}) + {\tau}_k^{(i)} \, \| \mbf{z} - \mbf{z}^{(i)}_{k} \|^2_2 \eqsub \label{mod_obj} 
\end{IEEEeqnarray}
where \eqn{\mbf{z}} is a vector stacking all optimization variables, which can be either \eqn{[\mx,\iter{\my}{\lpoint}{i-1},\mz]} or \eqn{[\iter{\mx}{\lpoint}{i},\my,\mz]} depending on the problem and \eqn{\mbf{z}^{(i)}_{k} \triangleq [\mx_{k}^{(i)},\iter{\my}{\lpoint}{i-1},\mz_{k}^{(i)}]} is the solution obtained in the previous \eqn{\ith{(k-1)}} \ac{SCA} step. The positive constant \me{{\tau}_{k}^{(i)} > 0} ensures strong convexity of \eqn{f} in each step \cite[Sec. 3.4.3]{bertsekas1989parallel}. Thus, due to strong convexity in \eqn{f}, uniqueness of the minimizer is ensured in each \ac{SCA} step \cite{yang_yang,scutari-1}.

\subsection{Bounded Objective Function and Compact Feasible Set} \label{b_obj}
The feasible set of problems \eqref{eqn-6} and \eqref{eqn-mse-1} is bounded and closed due to the total power constraint on transmit precoders by \eqref{eqn-6.4} and \eqref{eqn-mse-1.4}, therefore, the feasible region is compact.

@@

\subsection{Strict Monotonicity of the Objective Sequence} \label{mcity}
In the following discussions, we consider the modified objective \eqn{f} in \eqref{mod_obj} instead of \eqn{\hat{f}} to exploit the uniqueness of the minimizer at each iteration. However, we note that upon convergence \eqn{f} is equal to \eqn{\hat{f}}. Therefore, the discussions are valid for the \ac{JSFRA} problems in \eqref{eqn-6} and \eqref{eqn-mse-1} by regularizing the objective functions \eqref{eqn-6.1} and \eqref{eqn-mse-1.1} as \eqref{mod_obj}.

@@

where \eqn{c > 0} be the constant of strong convexity, defined as \eqn{c \triangleq \min_{k} \{{\tau}_{k}^{(i)}\}}, and \eqn{\iter{\mbf{z}}{k+1}{i}} is the solution. Therefore, by using \eqref{strict_monotonicity} and \eqn{\iter{\mbf{z}}{k}{i} \in \iter{\mc{X}}{k}{i}}, we can show that \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})} holds strictly in each \ac{SCA} step unless \eqn{\mbf{z}_{k}^{(i)} \to \mbf{z}_{\lpoint}^{(i)}} as \eqn{k \to \infty}. Now, by utilizing the facts that (i) \eqn{\{f(\mbf{z}^{(i)}_k)\}} is monotonic, and (ii) the uniqueness of the minimizer (see \eqref{strict_monotonicity}), strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}} is ensured in every \ac{SCA} update \cite{scutari2010convex}. \reviewF{Since the objective is strictly decreasing and bounded, convergence of \eqn{\{f(\mbf{z}_k^{(i)})\}} is guaranteed in every \ac{AO} step \eqn{i}. Let \eqn{\mbf{z}_{\lpoint}^{(i)} \triangleq \{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}\}} be the solution obtained upon convergence of the objective sequence in the \eqn{\ith{i}} \ac{AO} update.}

@@

Finally, to prove the global convergence of the \reviewF{objective sequence}, we need to show that the \ac{AO} updates also produce a nonincreasing sequence of objectives, \textit{i.e.}, 
\iftoggle{single_column}{
\begin{equation}
f(\iter{\mx}{\lpoint}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}).
\end{equation}}{
\begin{equation}
f(\iter{\mx}{\lpoint}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}).
\end{equation}}
Let \me{\iter{\mx}{\lpoint}{i}} and \me{\iter{\mz}{\lpoint|\my}{i}} be the solution obtained by solving \eqref{con-m} iteratively until \ac{SCA} convergence in the \me{\ith{i}} \ac{AO} iteration for \eqn{\mx} and \eqn{\mz} with fixed \eqn{\my = \iter{\my}{\lpoint}{i-1}}. To find \me{\iter{\my}{0}{i}}, we fix \eqn{\mx} as \me{\iter{\mx}{\lpoint}{i}} and optimize for \me{\my}. Since the constraint \eqref{con-dc-m} is linearized around \eqn{\iter{\mbf{z}}{\lpoint}{i}}, the fixed operating point is also included in the feasible set by following \eqref{con-sub-set} as \eqn{\{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}\} \in \iter{\mc{Y}}{0}{i}}, therefore, we have
\begin{equation} \label{fixed_point}
f(\iter{\mx}{\lpoint}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}).
\end{equation}
\reviewF{Now, by using \eqref{con-dc-m}, we can ensure that \eqn{\iter{\mbf{z}}{\lpoint}{i} \in \{ \iter{\mc{X}}{\lpoint}{i} \cap \iter{\mc{Y}}{0}{i} \}} in each \ac{AO} update \eqn{i} while alternating the optimization variables from \eqn{\mx,\mz} to \eqn{\my,\mz}. Moreover, due to strong convexity of the objective function \eqref{mod_obj}, by following \eqref{strict_monotonicity}, we can show that \eqref{fixed_point} holds with strict inequality in each \ac{AO} update unless the overall objective sequence converges. Now, by combining \eqref{con-convergence}, \eqref{strict_monotonicity} and \eqref{fixed_point}, we can ensure strictly nonincreasing nature of the objective sequence \eqn{\{f(\mbf{z}^{(i)}_k)\}} in every \ac{SCA} and \ac{AO} step.}

\subsection{Stationarity of Limit Points} \label{c-b}
\reviewF{We discuss the convergence of the iterates generated by the iterative algorithm. In order to do that, let us use consider a single global indexing \eqn{t} to represent both \ac{SCA} step \eqn{k} and \ac{AO} index \eqn{i}. It corresponds to every \ac{AO} iterations and \ac{SCA} updates performed within each of the \ac{AO} step.
Using this unified index \eqn{t}, we denote iterate \eqn{\ma^{t}} as a vector stacking all optimization variables produced in every \ac{SCA} iteration \eqn{{k}} and \ac{AO} step \eqn{{i}}.

\review{By following the discussions in Appendices \ref{b_obj} and \ref{mcity}, the sequence \eqn{\{f(\ma^t)\}} generated by the algorithm is bounded and monotonically decreasing, therefore, by using \cite[Prop. A.3]{bertsekas1999nonlinear}, convergence of the sequence \eqn{\{f(\ma^t)\}} can be ensured. Unfortunately, such a claim cannot be made on the convergence of \eqn{\{\ma^t\}}. However, due to the compactness of feasible set, the sequence of iterates \eqn{\{\ma^t\}} is bounded. Therefore, we can only claim that there exists at least one subsequence that converges to a limit point in the feasible set \cite[Th. 3.6]{rudin1964principles}.}

@@

Now, by using strict monotonicity of \eqn{\{f(\ma^{t_j})\}}, it follows that as \eqn{j \to \infty}, \eqn{\ma^{t_j} \to \bar{\ma}} and \eqn{f(\ma^{t_{j}}) - f(\ma^{t_{j+1}}) \to 0}. Moreover, since \eqn{\bar{\ma}} is the solution of \eqref{con-m}, it satisfies \eqref{strict_monotonicity} over convex subset \eqn{\mc{Q}}, which can either be \eqn{\iter{\mc{X}}{k}{i}} or \eqn{\iter{\mc{Y}}{k}{i}} as \eqn{k \to \infty, i \to \infty}. Using the above statements, we can show that \eqn{\bar{\ma}} satisfies the optimality condition  \cite[Prop. 2.1.2]{bertsekas1999nonlinear} as 
\begin{equation} \label{seq_mon1}
\nabla f (\bar{\ma})^\tran (\ma - \bar{\ma}) \geq 0, \; \fall \ma \in \mc{Q} \subset \mc{F} \eqsub.
\end{equation}
\review{Hence, \eqn{\bar{\ma}} is a stationary point and by using \eqref{limpoint}, we can show that every limit point of \eqn{\{\ma^t\}} is a stationary point. 
%In order to ensure the convergence of \eqn{\{\hat{f}(\ma^t)\}}, let us consider an instant \eqn{t} in which \eqn{\mat{t+1}} is the minimizer of \eqref{con-m}. Then, by using \eqref{mod_obj} and \eqref{strict_monotonicity}, monotonicity of \eqn{\{\hat{f}(\ma^t)\}} is shown by using \eqref{mod_obj} as
%\begin{equation} \label{mcity_origfunc}
%\hat{f}(\mat{t+1}) + \tau^t \|\mat{t+1} - \mat{t} \| \leq \hat{f}(\mat{t}) + \tau^t \|\mat{t} - \mat{t} \|
%\end{equation}
%where \eqn{\tau^t} is as in \eqref{mod_obj}. Additionally, by using Appendix \ref{c-a}, convergence of \eqn{\{\hat{f}(\ma^t)\}} can be established by \cite[Prop. A.3]{bertsekas1999nonlinear}.
}

\review{Before proceeding further, we ensure the convergence of \eqn{\{\hat{f}(\ma^t)\}} by showing that \eqn{\{\hat{f}(\ma^t)\}} is decreasing in every update and it is bounded. To do so, let us consider the minimizers \eqn{\mat{t}} and \eqn{\mat{t+1}} of problem \eqref{con-m} in iterations \eqn{{t-1}} and \eqn{{t}}, respectively. Since the proximal term in \eqref{mod_obj} is given as \eqn{\|\mat{} - \mat{t}\|^2} for iteration \eqn{t}, the relation between \eqn{\mat{t}} and \eqn{\mat{t+1}} satisfies
\begin{equation} \label{mcity_origfunc}
\hat{f}(\mat{t+1}) + \tau^t \|\mat{t+1} - \mat{t} \|^2 \leq \hat{f}(\mat{t}) + \tau^t \|\mat{t} - \mat{t} \|^2
\end{equation}
where \eqn{\tau^t} denotes \eqn{\tau_k^{(i)}} in \eqref{mod_obj} and \eqn{\|\mat{t+1} - \mat{t} \|^2 \geq 0}. Thus, by extending \eqref{mcity_origfunc} to every update and by using Appendix \ref{b_obj}, convergence of \eqn{\{\hat{f}(\ma^t)\}} can be shown using \cite[Prop. A.3]{bertsekas1999nonlinear}.}

>>>>

The following conditions are required to show the convergence of Algorithm \ref{algo-1}, which is used to solve problems \eqref{eqn-6} and \eqref{eqn-mse-1} in an iterative manner.
\begin{itemize}
\item[(a)] Uniqueness of the minimizer in each step
\item[(b)] Objective function should be bounded below
\item[(c)] Feasible set should be compact
\item[(d)] Sequence of objective values should be strictly decreasing
\end{itemize}
Note that the uniqueness condition in (a) is required to ensure strict monotonicity in the objective sequence. Upon satisfying (a)-(d), we can show the convergence of the objective sequence generated by the Algorithm \ref{algo-1}, using \cite[Th. 3.14]{rudin1964principles}. Then, by following the discussions in \cite{marks1978technical,lanckriet2009convergence,scutari_1}, we can claim that \reviewF{every limit point of the sequence of iterates generated by the iterative method is a stationary point of original nonconvex formulations in \eqref{eqn-6} and \eqref{eqn-mse-1}}.

@@

\subsection{Uniqueness of the Iterates and Strong Convexity} \label{c-a}
The uniqueness of the iterates \eqn{\{\iter{\mx}{k}{i},\iter{\my}{\lpointx}{i-1},\iter{\mz}{k|\my}{i}\}} can be ensured for the \ac{MSE} reformulated problem in \eqref{eqn-mse-2} when all the constraints are active. However, if \eqn{\hat{f}(\iter{\mx}{k}{i},\iter{\my}{\lpointx}{i-1},\iter{\mz}{k|\my}{i}) = 0} after some iteration, say \me{k} and \me{i}, then the uniqueness is not ensured as there can be multiple solutions in the feasible set.

To ensure the uniqueness of transmit and receive beamformers in each iteration, the objective function of subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} are regularized by a strongly convex function in each \ac{SCA} iteration \eqn{k} and \ac{AO} update step \eqn{i} as 
\begin{IEEEeqnarray}{rCl} \neqsub
\hat{f}(\mbf{z}) &=& \| \tilde{\mbf{v}} \|_q \eqsub \label{orig_obj} \\ 
f(\mbf{z}) &=& \hat{f}(\mbf{z}) + {\tau}_k^{(i)} \, \| \mbf{z} - \mbf{z}^{(i)}_{k} \|^2_2 \eqsub \label{mod_obj} 
\end{IEEEeqnarray}
where \eqn{\mbf{z}} is a vector formed by stacking all optimization variables that can be either \eqn{[\mx,\iter{\my}{\lpoint}{i-1},\mz]} or \eqn{[\iter{\mx}{\lpoint}{i},\my,\mz]} depending on the variables that are fixed. Moreover, \eqn{\mbf{z}^{(i)}_{k} \triangleq [\mx_{k}^{(i)},\iter{\my}{\lpoint}{i-1},\mz_{k}^{(i)}]} is the solution obtained on the \eqn{\ith{(k-1)}} \ac{SCA} step of \ac{AO} update instant \eqn{i}. The positive constant \me{{\tau}_{k}^{(i)} > 0} ensures strong convexity of \eqn{f} in each step \cite[Sec. 3.4.3]{bertsekas1989parallel}. Thus, due to strong convexity in \eqn{f}, uniqueness of the minimizer is ensured in each \ac{SCA} step \cite{yang_yang,scutari-1}.

\subsection{Bounded Objective Function and Compact Feasible Set} \label{b_obj}
The feasible set of problems \eqref{eqn-6} and \eqref{eqn-mse-1} is bounded and closed due to the total power constraint on the transmit precoders by the constraints \eqref{eqn-6.4} and \eqref{eqn-mse-1.4}, therefore, the feasible region is compact.

@@

\subsection{Strict Monotonicity of the Objective Sequence} \label{mcity}
In the following discussions, we consider the modified objective \eqn{f(\mbf{z})} in \eqref{mod_obj} instead of \eqn{\hat{f}(\mbf{z})} to exploit the uniqueness of the minimizer at each iteration. However, note that upon convergence \eqn{f(\mbf{z})} is equal to \eqn{\hat{f}(\mbf{z})}. Therefore, the discussions are valid for the \ac{JSFRA} problems in \eqref{eqn-6} and \eqref{eqn-mse-1} by regularizing the objective functions \eqref{eqn-6.1} and \eqref{eqn-mse-1.1} as \eqref{mod_obj}.

@@

where \eqn{c > 0} be the constant of strong convexity, defined as \eqn{c \triangleq \min_{k} \{{\tau}_{k}^{(i)}\}}, and \eqn{\iter{\mbf{z}}{k+1}{i}} is the solution. Therefore, by using \eqref{strict_monotonicity} and \eqn{\iter{\mbf{z}}{k}{i} \in \iter{\mc{X}}{k}{i}}, we can show that \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})} holds strictly in each \ac{SCA} step unless \eqn{\mbf{z}_{k}^{(i)} \to \mbf{z}_{\lpoint}^{(i)}} as \eqn{k \to \infty}. Now, by utilizing the facts that (i) \eqn{\{f(\mbf{z}^{(i)}_k)\}} is monotonic, and (ii) the uniqueness of the minimizer (see \eqref{strict_monotonicity}), strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}} is ensured in each \ac{SCA} update \cite{scutari2010convex}. \reviewF{Since the objective is strictly decreasing and bounded, convergence of \eqn{\{f(\mbf{z}_k^{(i)})\}} is guaranteed in each \ac{AO} step \eqn{i}. Let \eqn{\mbf{z}_{\lpoint}^{(i)} \triangleq \{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}\}} be the solution obtained upon convergence of the objective sequence in the \eqn{\ith{i}} \ac{AO} update.}

@@

Finally, to prove the global convergence of the \reviewF{objective sequence}, we need to show that the \ac{AO} updates also produce a nonincreasing sequence of objectives, \textit{i.e.}, 
\iftoggle{single_column}{
\begin{equation}
f(\iter{\mx}{\lpoint}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}).
\end{equation}}{
\begin{equation}
f(\iter{\mx}{\lpoint}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}).
\end{equation}}
Let \me{\iter{\mx}{\lpoint}{i}} and \me{\iter{\mz}{\lpoint|\my}{i}} be the solution obtained by solving \eqref{con-m} with respect to \eqn{\mx} and \eqn{\mz} by performing \ac{SCA} update as \eqn{k \to \infty} in the \me{\ith{i}} \ac{AO} step with fixed \eqn{\my = \iter{\my}{\lpoint}{i-1}}. In order to find \me{\iter{\my}{0}{i}}, we fix \eqn{\mx} as \me{\iter{\mx}{\lpoint}{i}} and solve problem \eqref{con-m} for \me{\my} and \eqn{\mz}. Since the constraint \eqref{con-dc-m} is linearized around \eqn{\iter{\mbf{z}}{\lpoint}{i}}, the fixed operating point is also included in the feasible set by following \eqref{con-sub-set} as \eqn{\{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}\} \in \iter{\mc{Y}}{0}{i}}, therefore, we have
\begin{equation} \label{fixed_point}
f(\iter{\mx}{\lpoint}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}).
\end{equation}
\reviewF{Now, by using \eqref{con-dc-m}, we can ensure that \eqn{\iter{\mbf{z}}{\lpoint}{i} \in \{ \iter{\mc{X}}{\lpoint}{i} \cap \iter{\mc{Y}}{0}{i} \}} in each \ac{AO} update \eqn{i} while alternating the optimization variables from \eqn{\mx,\mz} to \eqn{\my,\mz}. Moreover, due to strong convexity of the objective function \eqref{mod_obj}, by following \eqref{strict_monotonicity}, we can show that \eqref{fixed_point} holds with strict inequality in each \ac{AO} update unless the overall objective sequence converges. Now, by combining \eqref{con-convergence}, \eqref{strict_monotonicity} and \eqref{fixed_point}, we can ensure strictly nonincreasing nature of the objective sequence \eqn{\{f(\mbf{z}^{(i)}_k)\}} in each \ac{SCA} and \ac{AO} step.}

\subsection{Stationarity of Limit Points} \label{c-b}
\reviewF{We now discuss the convergence properties of the sequence of iterates generated by the proposed algorithm. For convenience, let us consider a unified superscript index \eqn{t} to refer to the index of both \ac{SCA} and \ac{AO} procedures (\textit{i.e.}, index \eqn{t} denotes \ac{SCA} and \ac{AO} update step (\eqn{k,i})). Using this, we denote iterate \eqn{\ma^t} as a stacked vector of the minimizer obtained by solving \eqref{con-m} at each step \eqn{t} as \eqn{\mat{t} = \mbf{z}^{(i)}_k} for some \ac{SCA} and \ac{AO} iteration.
%Furthermore, we introduce variable \eqn{\ma^{t}} to denote a vector formed by stacking solution obtained at \eqn{\ith{t}} iteration, \textit{i.e.}, \eqn{\mat{t} = \mbf{z}^{(i)}_k}, the respective iterate.

The objective sequence \eqn{\{f(\ma^t)\}} generated by the algorithm is bounded and monotonically decreasing (see Appendices \ref{b_obj} and \ref{mcity}). Therefore, by using \cite[Prop. A.3]{bertsekas1999nonlinear}, the convergence of the sequence \eqn{\{f(\ma^t)\}} can be ensured. Unfortunately, such a claim cannot be made on the convergence of sequence of iterates \eqn{\{\ma^t\}}. However, since the feasible set is compact, the sequence \eqn{\{\ma^t\}} is bounded. Therefore, the sequence \eqn{\{\ma^t\}} has at least one limit point, say \eqn{\bar{\mbf{x}}}, such that there exists a subsequence of \eqn{\{\ma^t\}} that converges to \eqn{\bar{\mbf{x}}} \cite[Prop. A.5]{bertsekas1999nonlinear}.

@@

Now, by using strict monotonicity of \eqn{\{f(\ma^{t_j})\}}, it follows that as \eqn{j \to \infty}, \eqn{\ma^{t_j} \to \bar{\ma}} and \eqn{f(\ma^{t_{j}}) - f(\ma^{t_{j+1}}) \to 0}. Moreover, since \eqn{\bar{\ma}} is the solution of \eqref{con-m}, it satisfies \eqref{strict_monotonicity} over convex subset \eqn{\mc{Q}}, which can either be \eqn{\iter{\mc{X}}{k}{i}} or \eqn{\iter{\mc{Y}}{k}{i}} as \eqn{k \to \infty, i \to \infty}. Using the above statements, we can show that \eqn{\bar{\ma}} satisfies the optimality condition  \cite[Prop. 2.1.2]{bertsekas1999nonlinear} as 
\begin{equation} \label{seq_mon1}
\nabla f (\bar{\ma})^\tran (\ma - \bar{\ma}) \geq 0, \; \fall \ma \in \mc{Q} \subset \mc{F} \eqsub.
\end{equation}
Hence, \eqn{\bar{\ma}} is a stationary point and by using \eqref{limpoint}, we can show that every limit point of \eqn{\{\ma^t\}} is a stationary point of \eqref{con-m}.

Before proceeding further, we also ensure the convergence of \eqn{\{\hat{f}(\ma^t)\}} by showing that the original objective function in \eqref{orig_obj} also decreases at each iteration. To do so, let us consider the minimizers \eqn{\mat{t}} and \eqn{\mat{t+1}} of problem \eqref{con-m} in iterations \eqn{{t-1}} and \eqn{{t}}, respectively. Since \eqn{\|\mat{} - \mat{t}\|^2} is the proximal term in \eqref{mod_obj} for iteration \eqn{t}, the relation between \eqn{\mat{t}} and \eqn{\mat{t+1}} satisfies
\begin{equation} \label{mcity_origfunc}
\hat{f}(\mat{t+1}) + \tau^t \|\mat{t+1} - \mat{t} \|^2 \leq \hat{f}(\mat{t}) + \tau^t \|\mat{t} - \mat{t} \|^2
\end{equation}
where \eqn{\tau^t} denotes \eqn{\tau_k^{(i)}} in \eqref{mod_obj} and \eqn{\|\mat{t+1} - \mat{t} \|^2 \geq 0}. Thus, by extending \eqref{mcity_origfunc} to every update and by using Appendix \ref{b_obj}, convergence of \eqn{\{\hat{f}(\ma^t)\}} can be shown using \cite[Prop. A.3]{bertsekas1999nonlinear}.

### 2015-11-24 Report/convergence_distributed.tex
updated and finalized

\reviewF{Convergence of the primal decomposition and the \ac{ADMM} follow the same discussions as in Appendix \ref{sec-3.5}, if in each \ac{SCA} step, the distributed schemes converge to the centralized solution. To show that, let us consider subproblem \eqref{eqn-decent-1} in the \eqn{\ith{k}} \ac{SCA} step, solved by distributed method using a regularized objective as in \eqref{mod_obj}. At first, the convergence of the primal decomposition method is discussed by using following properties. (i) The feasible set is non-empty and bounded, therefore, each subproblem satisfies the Slater's constraint qualifications. (ii) Due to strong convexity of the objective \eqref{mod_obj} in subproblem, the minimizer is unique. \review{Therefore, by using the above facts, as \eqn{j \to \infty}, the convergence of the primal decomposition can be shown using \cite[Prop. 8.2.6]{bertsekas2003convex} for a diminishing step size in each subgradient update.}}

>>>>

\reviewF{Convergence of the primal decomposition and the \ac{ADMM} follow the same discussions as in Appendix \ref{sec-3.5}, if in each \ac{SCA} step, the distributed schemes converge to the centralized solution. To show that, let us consider subproblem \eqref{eqn-decent-1} in the \eqn{\ith{k}} \ac{SCA} step, solved by distributed method using a regularized objective as in \eqref{mod_obj}. At first, the convergence of the primal decomposition method is discussed by using following properties. (i) The feasible set is non-empty and bounded, therefore, each subproblem satisfies the Slater's constraint qualifications. (ii) Due to strong convexity of the objective \eqref{mod_obj} in subproblem, the minimizer is unique. Therefore, by using the above facts and as \eqn{j \to \infty}, the convergence of the primal decomposition method follows \cite[Prop. 8.2.6]{bertsekas2003convex} by using diminishing step size in each subgradient update.}

### 2015-11-24 Report/dual_approach.tex
updated and finalized

\reviewF{Assuming that the following conditions are satisfied by the distributed schemes in every \ac{SCA} step, \textit{i.e.}, (i) by ensuring the uniqueness of the minimizer, and (ii) the distributed methods are performed for \eqn{j \to \infty}, convergence analysis follow the discussions in Appendices \ref{sec-3.5} and \ref{sec-dist-conv}. Moreover, the convergence discussions in Appendices \ref{sec-3.5} and \ref{sec-dist-conv} are valid even if the receivers are updated together with the transmit precoders as in Algorithm \ref{algo-3}, since strict monotonic decrease of the objective sequence can still be ensured. The reason is that the \ac{MMSE} receiver is optimal for the fixed transmit precoders obtained after each \ac{SCA} update. However, in practice, to reduce the amount of information exchange among the coupling \acp{BS}, often distributed schemes are iterated for limited number of iterations, say, for \eqn{J_{\max}} only. In such a case, convergence of the distributed algorithms cannot not be ensured, since it is difficult to show that the objective value is monotonically decreasing at every \ac{SCA} step. It follows from the fact that in each primal or \ac{ADMM} update, the global objective cannot be guaranteed to decrease monotonically.}

>>>>

\reviewF{Assuming that the following conditions are satisfied by the distributed schemes in every \ac{SCA} step, \textit{i.e.}, (i) by ensuring the uniqueness of the minimizer, and (ii) the distributed methods are performed for \eqn{j \to \infty}, convergence analysis follows the discussions in Appendices \ref{sec-3.5} and \ref{sec-dist-conv}. Moreover, the convergence discussions in Appendices \ref{sec-3.5} and \ref{sec-dist-conv} are valid even if the receivers are updated together with the transmit precoders as in Algorithm \ref{algo-3}, since strict monotonic decrease of the objective sequence can still be ensured. The reason is that the \ac{MMSE} receiver is optimal for the fixed transmit precoders obtained after each \ac{SCA} update. However, in practice, to reduce the amount of information exchange among the coupling \acp{BS}, often distributed schemes are iterated for limited number of iterations, say, for \eqn{J_{\max}} only. In such a case, convergence of the distributed algorithms cannot not be ensured, since it is impossible to show that the objective value is monotonically decreasing at every \ac{SCA} step. We recall that in each primal or \ac{ADMM} update, the global objective cannot be guaranteed to decrease monotonically.}

### 2015-11-24 Report/mse_formulation.tex
updated and finalized

In all our simulations, the objective sequence generated by the Algorithm \ref{algo-1} converges. \reviewF{However, for a formal convergence analysis, we consider a regularized objective in \eqref{mod_obj} instead of \eqref{eqn-6.1} and \eqref{eqn-mse-1.1}. The proximal term in \eqref{mod_obj} ensures strong convexity, thereby enforcing the uniqueness of the minimizer in each step. Note that the feasible set of problems \eqref{eqn-3} and \eqref{eqn-mse-1} is bounded. However, for \eqref{eqn-6}, the feasible set need not be bounded due to newly introduced variables in \eqref{eqn-6.2} and \eqref{eqn-6.3} to relax \eqref{eq:SINR}, since \eqn{\beta_{l,k,n}} can assume any value satisfying \eqref{eqn-6.3} without violating any other constraints in \eqref{eqn-6} when \eqn{\gamma_{l,k,n} = 0}. Therefore, by restricting \eqn{\beta_{l,k,n}}'s with a maximum interference constraint depending on \eqn{P_{\max}}, the feasible set can be bounded without altering the solution space of other variables. However, as a consequence of considering the regularized objective in \eqref{mod_obj}, the additional constraint on \eqn{\beta_{l,k,n}} is not required, since it is bounded due to the proximal term in \eqref{mod_obj}. With the above assumptions, convergence proof is presented in Appendix \ref{sec-3.5}.}

>>>>

In all our numerical simulations, the objective sequence generated by the Algorithm \ref{algo-1} converges. \reviewF{However, to provide a formal convergence analysis, we consider a regularized objective in \eqref{mod_obj} instead of \eqref{eqn-6.1} and \eqref{eqn-mse-1.1}. The proximal term in \eqref{mod_obj} ensures strong convexity, thereby enforcing the uniqueness of the minimizer in each iteration. Note that the feasible set of problems \eqref{eqn-3} and \eqref{eqn-mse-1} is bounded. However, for problem \eqref{eqn-6}, the feasible set need not be bounded due to newly introduced variables in \eqref{eqn-6.2} and \eqref{eqn-6.3} to relax the \ac{SINR} expression in \eqref{eq:SINR}, since \eqn{\beta_{l,k,n}} can assume any value satisfying \eqref{eqn-6.3} without violating any other constraints in \eqref{eqn-6} when \eqn{\gamma_{l,k,n} = 0}. Nevertheless, we can limit \eqn{\beta_{l,k,n}}'s by using a maximum interference threshold depending on \eqn{P_{\max}} and the channel gains, and thus the feasible set can be bounded without affecting the optimality of the considered problem. By using the above assumptions, convergence analysis for the centralized problem is discussed in Appendix \ref{sec-3.5}.}
